\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-25 OaklandSubmission/intro.tex
nit

%\item
The third option for Alice is to earn a PhD in cryptography and design
specialized, efficient protocols (similar to
~\cite{shafindss,wu,minionn}) for her tasks.
%\end{tiret}
%In our work, we achieve the best of all the above options.

>>>>

%\item
The third option for Alice is to earn a PhD in cryptography and design
specialized, efficient \mpc protocols (similar to
~\cite{shafindss,wu,minionn}) for her tasks.
%\end{tiret}
%In our work, we achieve the best of all the above options.
